---
title: "Homework 1: ggplot2"
author: "Monika Stoljarova"
date: "2019-03-04"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
```

By using *mpg* dataset:

1. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

- Color
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x=cty, y=hwy, color=hwy))
```

- Size
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x=cty, y=hwy, size=hwy))
```

- Shape
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x=cty, y=hwy, shape=class))+scale_shape_manual(values=1:7)
```
MS: It is not possible to map shape to a continues variable. At least this is what the RStudio says.




2. What happens if you map the same variable to multiple aesthetics?

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x=cty, y=hwy, color=class, size=class, shape=class)) + scale_shape_manual(values=1:7
                                                                                                                      )

```
MS: Each of the variable point get a different, coclor, size and shape. Very vibrant. 





3. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x=cty, y=hwy, shape=class), stroke=3)+scale_shape_manual(values=1:7)
```
MS: Stoke changes the thinkness of shape's symple wall





4. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x=cty, y=hwy, color = displ < 5))
```
MS: the aestetic is applied to the specified value. In our case disp <5 is seperataly colored than disp >=5

